Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-22 paper.qmd
chore: update `Acknowledgments`
chore: replace `buildInputs` with `packages`

```{=tex}
\begin{CodeInput}
let
  pkgs = import (fetchTarball
    "https://github.com/NixOS/nixpkgs/archive/976fa336.tar.gz"
  ) {};
  system_packages = builtins.attrValues {
    inherit (pkgs) R;
  };
in
  pkgs.mkShell {
    buildInputs = [ system_packages ];
    shellHook = "R --vanilla";
  }
\end{CodeInput}
```

@@

I thank the rOpenSci reviewers and contributors who provided valuable feedback
on the development of [rix]{.pkg} and [rixpress]{.pkg}. In particular, I am
grateful to David Watkins and Jacob Wujiciak-Jens for their reviews of [rix]{.pkg},
and to William Landau and Anthony Martinez for their reviews of [rixpress]{.pkg}. I
also acknowledge the contributions of Philipp Baumann, [rix]{.pkg}’s co-author,
Richard J. Acton, Jordi Rosell, Elio Campitelli, László Kupcsik, and
Michael Heming for [rix]{.pkg}. Their expertise and feedback greatly
improved the quality and usability of these packages.

>>>>

```{=tex}
\begin{CodeInput}
let
  pkgs = import (fetchTarball
    "https://github.com/NixOS/nixpkgs/archive/976fa336.tar.gz"
  ) {};
  system_packages = builtins.attrValues {
    inherit (pkgs) R;
  };
in
  pkgs.mkShell {
    packages = [ system_packages ];
    shellHook = "R --vanilla";
  }
\end{CodeInput}
```

@@

I thank the rOpenSci reviewers and contributors who provided valuable feedback
on the development of [rix]{.pkg} and [rixpress]{.pkg}. In particular, I am
grateful to David Watkins and Jacob Wujiciak-Jens for their reviews of [rix]{.pkg},
and to William Landau and Anthony Martinez for their reviews of [rixpress]{.pkg}. I
also acknowledge the contributions of Philipp Baumann, [rix]{.pkg}’s co-author,
Richard J. Acton, Jordi Rosell, Elio Campitelli, László Kupcsik, Pol Dellaiera, and
Michael Heming for [rix]{.pkg}. Their expertise and feedback greatly
improved the quality and usability of these packages.
